\paperTitle

### 2014-06-19 doc/icml2014/icml2014-presentation/diagrams.tex

@@

   \draw[-latex] (h2) -- (x2);
   \draw[-latex] (h2) -- (x3);
   \draw[-latex] (h2) -- (x4);
   \draw[-latex] (h2) -- (x5);
   }
}

\newcommand{\tensorfactorization}[1]{%
  \point{start-tf}{#1}
  \tikzcube{tensoring}{black,fill=white}{($(start-tf) + (0,0,0)$)}{1}{1}{1};
  \node at ($(tensoring) + (1.0cm,-0.3cm)$) {$=$};
  \tensorfiber{t1}{fill=blue!70}{($(tensoring) + (2.5cm,0.0cm)$)};
  \node at ($(t1) + (1.0cm,-0.3cm)$) {$+$};
  \tensorfiber{t2}{fill=green!70}{($(t1) + (2.5cm,0.0cm)$)};
  \node at ($(t2) + (1.0cm,-0.3cm)$) {$+ \dots + $};
  \tensorfiber{t3}{fill=red!70}{($(t2) + (3.0cm,0.0cm)$)};

@@

\newcommand{\matrixfactorization}[1]{%
    \point{start-mf}{#1}
    \tikzrect{mat}{black,fill=white}{($(start-mf) + (0,0)$)}{1}{1};
    \node at ($(mat) + (1.0cm,-0.3cm)$) {$=$};
    \matfiber{t1}{fill=blue!70}{($(mat) + (2.5cm,0.0cm)$)};
    \node at ($(t1) + (1.0cm,-0.3cm)$) {$+$};
    \matfiber{t2}{fill=green!70}{($(t1) + (2.5cm,0.0cm)$)};
    \node at ($(t2) + (1.0cm,-0.3cm)$) {$+ \dots + $};
    \matfiber{t3}{fill=red!70}{($(t2) + (3.0cm,0.0cm)$)};
    \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt,mirror},yshift=0pt] 
      ($(t1) + (-1cm,-1cm)$) -- ($(t3) + (0.2cm,-1cm)$) node [below,black,midway,yshift=-0.6cm] {$k$};
}

\newcommand{\vectorfactorization}[1]{%
    \point{start-vf}{#1}
    \tikzrect{vec}{black,fill=white}{($(start-vf) + (0,0)$)}{0.3}{1};
    \node at ($(vec) + (1.0cm,-0.3cm)$) {$=$};
    \tikzrect{t1}{fill=blue!70}{($($(vec) + (2.5cm,0.0cm)$)$)}{0.3}{1};
    \node at ($(t1) + (1.0cm,-0.3cm)$) {$+$};
    \tikzrect{t2}{fill=green!70}{($($(t1) + (2.5cm,0.0cm)$)$)}{0.3}{1};
    \node at ($(t2) + (1.0cm,-0.3cm)$) {$+ \dots + $};
    \tikzrect{t3}{fill=red!70}{($($(t2) + (3cm,0.0cm)$)$)}{0.3}{1};
    \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt,mirror},yshift=0pt] 
      ($(t1) + (-1cm,-1cm)$) -- ($(t3) + (0.2cm,-1cm)$) node [below,black,midway,yshift=-0.6cm] {$k$};
}

>>>>

\newcommand<>{\drawgensquiggle}[1]{%
  \uncover#2{
    \point{start-gen}{#1}
    \node[style=node] (h) at (start-gen) {$h$};
%    \node[left=0.1cm of h] {$h$};
    \node[style=obsnode,below=1cm of h] (x2) {$x_2$};
    \node[style=obsnode,left=0.5cm of x2] (x1) {$x_1$};
    \node[style=obsnode,right=0.5cm of x2] (x3) {$x_3$};
    \draw[-latex,squiggle] (h) -- (x1);
    \draw[-latex,squiggle] (h) -- (x2);
    \draw[-latex,squiggle] (h) -- (x3);
  }
}

@@

   \draw[-latex] (h2) -- (x1);
   \draw[-latex] (h2) -- (x2);
   \draw[-latex] (h2) -- (x3);
   \draw[-latex] (h2) -- (x4);
   \draw[-latex] (h2) -- (x5);
   }
}

\newcommand<>{\drawbridge}[1]  {
  \uncover#2{
    \point{start-bridge}{#1};
    % Hidden nodes
   \node[style=node, scale=0.8] (h1) at (start-bridge) {$h_1$};
   \node[style=node, scale=0.8, right= 1.0cm of h1] (h2) {$h_2$};
   \draw[-latex] (h1) -- node[above] (h1h2) {} (h2);

% Observed nodes
   \node[style=obsnode, scale=0.6, below left=0.3cm of h1] (x1a) {$x_1^a$};
   \node[style=obsnode, scale=0.6, below=0.3cm of h1] (x1b) {$x_1^b$};
   \node[style=obsnode, scale=0.6, below=0.3cm of h2] (x2a) {$x_2^a$};
   \node[style=obsnode, scale=0.6, below right=0.3cm of h2] (x2b) {$x_2^b$};
   \draw[-latex] (h1) -- (x1a);
   \draw[-latex] (h1) -- (x1b);
   \draw[-latex] (h2) -- (x2a);
   \draw[-latex] (h2) -- (x2b);
   }
}

\newcommand<>{\drawubridge}[1]  {
  \uncover#2{
    \point{start-ubridge}{#1};
    % Hidden nodes
   \node[style=node, scale=0.8] (h1) at (start-ubridge) {$h_1$};
   \node[style=node, scale=0.8, right= 1.0cm of h1] (h2) {$h_2$};
   \draw[-] (h1) -- node[above] (h1h2) {} (h2);

% Observed nodes
   \node[style=obsnode, scale=0.6, below left=0.3cm of h1] (x1a) {$x_1^a$};
   \node[style=obsnode, scale=0.6, below=0.3cm of h1] (x1b) {$x_1^b$};
   \node[style=obsnode, scale=0.6, below=0.3cm of h2] (x2a) {$x_2^a$};
   \node[style=obsnode, scale=0.6, below right=0.3cm of h2] (x2b) {$x_2^b$};
   \draw[-] (h1) -- (x1a);
   \draw[-] (h1) -- (x1b);
   \draw[-] (h2) -- (x2a);
   \draw[-] (h2) -- (x2b);
   }
}

\newcommand{\tensorfactorization}[1]{%
  \point{start-tf}{#1}
  \tikzcube{tensoring}{black,fill=white}{($(start-tf) + (0,0,0)$)}{1}{1}{1};
  \node at ($(tensoring) + (1.0cm,-0.3cm)$) {$=$};
  \tensorfiber{t1}{fill=blue!70}{($(tensoring) + (2.5cm,0.0cm)$)};
  \node at ($(t1) + (1.0cm,-0.3cm)$) {$+$};
  \tensorfiber{t2}{fill=DarkGreen!70}{($(t1) + (2.5cm,0.0cm)$)};
  \node at ($(t2) + (1.0cm,-0.3cm)$) {$+ \dots + $};
  \tensorfiber{t3}{fill=red!70}{($(t2) + (3.0cm,0.0cm)$)};

@@

\newcommand{\matrixfactorization}[1]{%
    \point{start-mf}{#1}
    \tikzrect{mat}{black,fill=white}{($(start-mf) + (0,0)$)}{1}{1};
    \node at ($(mat) + (1.0cm,-0.3cm)$) {$=$};
    \matfiber{t1}{fill=blue!70}{($(mat) + (2.5cm,0.0cm)$)};
    \node at ($(t1) + (1.0cm,-0.3cm)$) {$+$};
    \matfiber{t2}{fill=DarkGreen!70}{($(t1) + (2.5cm,0.0cm)$)};
    \node at ($(t2) + (1.0cm,-0.3cm)$) {$+ \dots + $};
    \matfiber{t3}{fill=red!70}{($(t2) + (3.0cm,0.0cm)$)};
    \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt,mirror},yshift=0pt] 
      ($(t1) + (-1cm,-1cm)$) -- ($(t3) + (0.2cm,-1cm)$) node [below,black,midway,yshift=-0.6cm] {$k$};
}

\newcommand{\vectorfactorization}[1]{%
    \point{start-vf}{#1}
    \tikzrect{vec}{black,fill=white}{($(start-vf) + (0,0)$)}{0.3}{1};
    \node at ($(vec) + (1.0cm,-0.3cm)$) {$=$};
    \tikzrect{t1}{fill=blue!70}{($($(vec) + (2.5cm,0.0cm)$)$)}{0.3}{1};
    \node at ($(t1) + (1.0cm,-0.3cm)$) {$+$};
    \tikzrect{t2}{fill=DarkGreen!70}{($($(t1) + (2.5cm,0.0cm)$)$)}{0.3}{1};
    \node at ($(t2) + (1.0cm,-0.3cm)$) {$+ \dots + $};
    \tikzrect{t3}{fill=red!70}{($($(t2) + (3cm,0.0cm)$)$)}{0.3}{1};
    \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt,mirror},yshift=0pt] 
      ($(t1) + (-1cm,-1cm)$) -- ($(t3) + (0.2cm,-1cm)$) node [below,black,midway,yshift=-0.6cm] {$k$};
}
